
\documentclass{report}
\usepackage[top=0.7in, bottom=0.7in, left=2in, right=2in]{geometry} %for setting the margins
\usepackage{amsmath} % for the equation* environment
\usepackage{xcolor} % for the \textcolor command
\usepackage{tcolorbox} % for the tcolorbox environment
\renewcommand\thesection{\arabic{section}}  % Section numbers without chapter
\renewcommand\thesubsection{\thesection.\arabic{subsection}}
\setcounter{secnumdepth}{3} % Numbering subsubsections
\fontsize{14pt}{16pt}
\title{ Vim Notes \\}

\date{23/08/2024}
\author{Can Caliskan}
\begin{document}
  \maketitle
  \raggedright %makes it left aligned, usefull for not getting errors after using /newline
\tableofcontents %creates a table of content
\newpage
\section{Movement Commands}
\subsection{Basic Movement}
\begin{itemize}
\item `M`: Move to the middle of the screen.
\item `L`: Move to the bottom of the screen.
\item  `H`: Moves the cursor to the top of the screen.
\item `5gg` or `5G`: Go to line 5.
\item `fx`: Jump to the next occurrence of character x.
\item `j`, `k`: Move down and up respectively.
\item `h`, `l`: Move left and right respectively.
\item `5j`, `5k`: Move 5 lines down or up.
	\subsection{Line Navigation}
\item \$: End of the line.
\item 0: Beginning of the line.
\item \_: First character of the line.
	\subsection{Scrolling}
\item `Ctrl + e`: Scroll screen down one line.
\item `Ctrl + y`: Scroll screen up one line.
\item `Ctrl + f`: Scroll full page down.
\item `Ctrl + b`: Scroll full page up.
\item `Ctrl + d`: Scroll half page down.
\item `Ctrl + u`: Scroll half page up.

	\subsection{Word and Sentence Navigation}
\item `w`: Move forward word by word.
\item `b`: Move backward word by word.
\item `e`: Jump to the end of a word.
\item `f.`, `F.`: Move to the next/previous occurrence of the period.
\item `(`, `)`: Move up or down by sentence.
\item `{`, `}`: Move up or down by paragraph.
	\subsection{File Navigation}
\item `gg`: Go to the start of the file.
\item `G`: Go to the end of the file.
\item `10gg`: Go to line 10.
	\subsection{Cursor Positioning}
\item `H`, `M`, `L`: Move the cursor to the top, middle, or bottom of the screen.
\item `Ctrl + w + h/j/k/l`: Navigate between split windows.
	\section{Insert Mode}
	\subsection{Basic Insert Commands}
\item `i`: Insert before the cursor.
\item `a`: Insert after the cursor.
\item `I`: Insert at the beginning of the line.
\item `A`: Insert at the end of the line.
\item `o`: Open a new line below the current line.
\item `O`: Open a new line above the current line.	
	\subsection{. Text Manipulation}
\item `c`: Change a word.
\item `s`: Replace the current character.
\item `ci"`, `di(`: Change or delete inside quotes/parentheses.
	\section{Copy, Paste, and Undo}

	\subsection{Basic Operations}
\item `y`: Yank (copy).
\item `p`: Paste.
\item `yy`: Copy a line.
\item `u`: Undo the last change.
\item `Ctrl + r`: Redo the last undone change.
	\subsection{Deleting}
\item `diw`: Delete a word.
\item `dis`: Delete a sentence.
\item `dip`: Delete a paragraph.
\item `dd`: Delete a line.
\item `dtX.`: Delete up to but not including X.
	\section{Searching and Replacing}
	\subsection{. Searching}
\item `/`: Search forward.
\item `n`: Move to the next occurrence.
\item `N`: Move to the previous occurrence.
\item `*`: Search for the word under the cursor.
\item `?`: Backward search.
	\subsection{Replacing}
\item `:s/thee/the/g`: Replace "thee" with "the" in the current line.
\item `:%s/old/new/g`: Replace every occurrence of "old" with "new" in the whole file.
\item `:\#,\#s/old/new/g`: Replace within a specific range of lines.
	\subsection{ Bookmarks and Macros}
	\subsection{. Bookmarks}
\item `ma`: Mark bookmark "a".
\item `'a`: Go to bookmark "a".
\item `:marks`: List all bookmarks.
\item `:delmarks a`: Delete bookmark "a".
	\subsection{Macros}
\item `q + {letter}`: Start recording a macro.
\item `q`: Stop recording.
\item `@{letter}`: Replay macro.
\item `5@{letter}`: Replay macro 5 times.
	\section{Visual Mode}
	\subsection{. Basic Visual Mode}
\item `v`: Start visual mode.
\item `V`: Start visual line mode.
\item `Ctrl + v`: Start visual block mode.
\item `shift + v`: Highlight the whole line.
\item `shift + j`: Join the line below to the current line.
	\subsection{Text Selection}
\item `vi(`: Select inside parentheses.
\item `va(`: Select around parentheses.
\item `vip`: Select inside paragraph.
	\subsection{Visual Mode Editing}
\item `gv`: Re-select the last visual selection.
\item `U`: Uppercase the selected text.
\item `shift + ~`: Toggle case of the selected character.
	\section{Advanced Commands}
	\subsection{. Split Windows}
\item `Ctrl + w + s`: Split window horizontally.
\item `Ctrl + w + v`: Split window vertically.
\item `:new`: Open a new buffer.
\item `:tabe filename`: Open the file in a new tab.
	\subsection{Line Operations}
\item `J`: Join two lines.
\item `:m-2`: Move current line up by two lines.
\item `m+2`: Move current line down by two lines.
	\subsection{Registers}
\item `"3p`: Paste from the 3rd register.
\item `"7y`: Yank into the 7th register.
\item `:reg`: List all registers.
\item `put a`: Paste register "a" content.
	\subsection{Increment and Decrement}
\item `Ctrl + a`: Increment a number under the cursor.
\item `Ctrl + x`: Decrement a number under the cursor.
	\section{Plugin and Tools}
	\subsection{. Harpoon}
\item `qq`: Open Harpoon menu.
\item `qw`: Add Harpoon.
\item `leader + 1/2/3`: Navigate Harpoon marks.
\item `t1`, `t2`: Open terminal 1 and 2.

	\subsection{Oil.nvim}
- File management and navigation.
\item `-`: open file explorer.

\subsection{Other Useful Plugins}
\item `gitsigns`: Git integration.
\item `mason`: Manage language servers.
\item `Telescope`: Fuzzy finder.
\item `Glow`: Markdown viewer.
	\section{Miscellaneous}
	\subsection{. Clipboard and Registers}
\item `"*`: Access system clipboard.
\item `"3p`: Paste from register 3.

	\subsection{File Operations}
\item `:wqa`: Write and quit all files.
\item `ZZ`: Save and quit.
\item `ZQ`: Quit without saving.
\item `:!sort`: Sort selected lines.
\item `:! figlet`: ASCII art generator.

	\subsection{Other Shortcuts}
\item `Ctrl + z`: Suspend Neovim, `fg` to resume.
\item `Ctrl + s`: Open in split.
\item `gf`: Open file under cursor.
\item `gx`: Open link in browser.
\end{itemize}


\end{document}

